Innovative Technologies for and Observational Studies of Star and Planet Formation

### 2015-03-25 chSPIE_2014_ebeam/SPIE_2014_ebeam.tex
woohoo, it compiles!

%\usepackage[]{graphicx}
%\usepackage{subfig}
%\usepackage{booktabs}
%\usepackage{multirow}

@@

At the 2012 SPIE Astronomical Telescopes and Instrumentation meeting (volume 8450) we described the detailed performance of the immersion grating (part number CA-1a \cite{2012SPIE.8450E..2SG}) for the high resolution infrared spectrograph IGRINS \cite{2010SPIE.7735E..54Y}.  IGRINS saw first light at McDonald Observatory in March 2014.  Papers describing its performance appear in the current volume\cite{2014SPIE.CHANPARK.IGRINS, 2014SPIE.BROOKS.GRATINGS}.  The technical readiness of the immersion grating now rests on firm footing, and our group has now moved on to pushing the performance and design limitations of silicon diffractive optics.  The key limitation is phase coherence.  Phase coherence for a diffraction grating is the accuracy to which repeated grating facets are positioned to an integer multiple of $\sigma$, the groove constant (the desired constant spacing from groove to groove).  Specifically, the position, $x$ of the $n^{th}$ facet in a sequence of $N$ total facets is distributed as:

@@

One major open question is whether CA-1a meets its spectral ghost level specification.  Spectral ghosts are secondary images that arise from periodic facet positioning errors\cite{2007sdf..book.....J}. The ghosts in CA-1a where introduced from a cyclically varying position-dependent exposure dose in the UV photolithography patterning step.  The processing error causing the ghosts has since been eliminated.  As a result our most recent immersion grating prototypes show a dramatic reduction in high frequency spectral ghosts [this volume, talk number 9151-35]\cite{2014SPIE.BROOKS.GRATINGS}.  The ghost level depends on the amplitude of the error (cf. Equation 14 of Marsh et al. 2007\cite{2007ApOpt..46.3400M}):
\begin{eqnarray}
	\frac{I_g}{I_0}=[ \frac{2\pi n}{\lambda}A \sin{\delta} ]^2	 \label{eqn:GLevel}
\end{eqnarray}
where $I_g/I_0$ is the ghost level relative to the main peak, $\lambda/n$ is the wavelength scaled in the refractive index, and $A$ is defined in Equation \ref{eqn:Periodic}.  We predicted an in-immersion ghost level of $I_g/I_0 \sim2\times10^{-3}$ at 1.5 $\mu$m based on visible laser metrology\cite{2012SPIE.8450E..2SG}.  At the time of writing the IGRINS commissioning team has constrained ghost levels at $\lambda=1.5 \; \mu$m to $I_g/I_0 < 1\times10^{-2}$.  The limitation of a direct ghost level measurement is the need to deconvolve the slit diffraction ringing from the spectral point spread function.

\section{Motivations for direct writing Si immersion gratings}
We have determined experimentally that the lithographic transfer step is the most important determinant of the optical quality of Si immersion gratings.  The prior steps: orienting, polishing, passivating and resist-coating the monolithic substrates is now routine and our process control for these steps is sufficient to limit their contribution to the error budget to the point where they have no effect on the quality of the final gratings\cite{2007ApOpt..46.3400M, 2014SPIE.BROOKS.GRATINGS}.  The subsequent steps: development of the resist, reactive ion etching of the passivation layer, and anisotropic etching of the V-grooves similarly contribute little to the overall errors.  We therefore concentrate our efforts on finding more effective and accurate ways to carry out the transfer or patterning step.

>>>>

@@

At the 2012 SPIE Astronomical Telescopes and Instrumentation meeting (volume 8450) we described the detailed performance of the immersion grating (part number CA-1a \cite{2012SPIE.8450E..2SG}) for the high resolution infrared spectrograph IGRINS \cite{2010SPIE.7735E..54Y}.  IGRINS saw first light at McDonald Observatory in March 2014.  Papers describing its performance appear in the current volume\cite{2014SPIE.CHANPARK.IGRINS,2014SPIE.9151E..1GB}.  The technical readiness of the immersion grating now rests on firm footing, and our group has now moved on to pushing the performance and design limitations of silicon diffractive optics.  The key limitation is phase coherence.  Phase coherence for a diffraction grating is the accuracy to which repeated grating facets are positioned to an integer multiple of $\sigma$, the groove constant (the desired constant spacing from groove to groove).  Specifically, the position, $x$ of the $n^{th}$ facet in a sequence of $N$ total facets is distributed as:

@@

One major open question is whether CA-1a meets its spectral ghost level specification.  Spectral ghosts are secondary images that arise from periodic facet positioning errors\cite{2007sdf..book.....J}. The ghosts in CA-1a where introduced from a cyclically varying position-dependent exposure dose in the UV photolithography patterning step.  The processing error causing the ghosts has since been eliminated.  As a result our most recent immersion grating prototypes show a dramatic reduction in high frequency spectral ghosts [this volume, talk number 9151-35]\cite{2014SPIE.9151E..1GB}.  The ghost level depends on the amplitude of the error (cf. Equation 14 of Marsh et al. 2007\cite{2007ApOpt..46.3400M}):
\begin{eqnarray}
	\frac{I_g}{I_0}=[ \frac{2\pi n}{\lambda}A \sin{\delta} ]^2	 \label{eqn:GLevel}
\end{eqnarray}
where $I_g/I_0$ is the ghost level relative to the main peak, $\lambda/n$ is the wavelength scaled in the refractive index, and $A$ is defined in Equation \ref{eqn:Periodic}.  We predicted an in-immersion ghost level of $I_g/I_0 \sim2\times10^{-3}$ at 1.5 $\mu$m based on visible laser metrology\cite{2012SPIE.8450E..2SG}.  At the time of writing the IGRINS commissioning team has constrained ghost levels at $\lambda=1.5 \; \mu$m to $I_g/I_0 < 1\times10^{-2}$.  The limitation of a direct ghost level measurement is the need to deconvolve the slit diffraction ringing from the spectral point spread function.

\section{Motivations for direct writing Si immersion gratings}
We have determined experimentally that the lithographic transfer step is the most important determinant of the optical quality of Si immersion gratings.  The prior steps: orienting, polishing, passivating and resist-coating the monolithic substrates is now routine and our process control for these steps is sufficient to limit their contribution to the error budget to the point where they have no effect on the quality of the final gratings\cite{2007ApOpt..46.3400M,2014SPIE.9151E..1GB}.  The subsequent steps: development of the resist, reactive ion etching of the passivation layer, and anisotropic etching of the V-grooves similarly contribute little to the overall errors.  We therefore concentrate our efforts on finding more effective and accurate ways to carry out the transfer or patterning step.
